### 2014-02-14 paper/example.tex
conditions on label+fork; CSK -> CESK

@@

>>>>

Background talks about IFC calculus in general; here we talk about
embedding and give the precise semantics for the IFC embedding.

@@

Which rules do we want to talk about?

\begin{enumerate}
\item fork: most complicated; shows side-condition (what do we do with stores on fork?)
\item label:  shows side-condition (what can we label? same as fork, but empty/all stores)
\item unlabel: shows raising of label
\item sendMessage: will give type for (maybe encapsulate queue in env)
\end{enumerate}
